Supplementary Material for Asymmetry paper

### 2020-06-17 Supplementary/Sup_mat.Rmd
Updating sup mat
Addressing some of Alasdair's comments
Still need to respec the models so there's no intercept

```{r load data and source function Hoop Size, echo - FALSE}
# load model data 
load("../Analyses/Experiment_3_Hoop_size/data/model_data")

@@

Add in facet plots

```{r HoopSizeFacets, include=T, echo=F}
load("../Analyses/Experiment_3_Hoop_size/scratch/df_part2_norm")
df_hoopsize <- norm_dat
rm(norm_dat)

@@

### Prior Predictions

@@

```{r run-model-hoop-size-priors, echo = T, include = F, cache = TRUE}

# run model
Hoop_size_priors <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                        data = model_data,
                        family = "beta",
                        prior = c(set_prior("student_t(3, 0, 1)",
                                            coef = "norm_hoop_pos",
                                            class = "b"),
                                  set_prior("student_t(3,0,1)",
                                            class = "Intercept")),
                        cores = 2,
                        chains = 2,
                        iter = 5000,
                        warmup = 2500,
                        control = list(adapt_delta = .95, max_treedepth = 15),
                        sample_prior = "only")
```

```{r HoopSizePriors, include = T, echo = F, warning = F,  fig.asp = .45, fig.cap="_Prior predictions for the Hoop Size experiment_"}
# need to make a dataset
draws <- HS_draw_post(Hoop_size_priors, model_data)

plt_estimates <- draws$plt_estimates 
plt_estimates

@@

### Conditioning on the data

```{r run-model-Hoop-size, include = F, echo = T, cache = TRUE}

# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                    data = model_data,
                    family = "beta",
                    prior = c(set_prior("student_t(3, 0, 1)",
                                        coef = "norm_hoop_pos",
                                        class = "b"),
                              set_prior("student_t(3,0,1)",
                                        class = "Intercept")),
                    cores = 2,
                    chains = 2,
                    iter = 5000,
                    warmup = 2500,
                    control = list(adapt_delta = .95, max_treedepth = 15))

@@

The model results confirmed that participants in general had a bias towards standing closer to the small hoop (mean of `r round(HDI_all$mean, digits = 3)`, 95% HDPI of |`r round(HDI_all$lower, digits = 3)`, `r round(HDI_all$upper, digits = 3)`|). We can be reasonably confident about this results as the p(x > 0.5|data) = `r paste(round(p_above_5$above0_5, digits = 3)*100, "%", sep = "")`. This can be seen in the posterior in Figure \@ref(fig:PltHoopSizeEstimates). Also, not that distance did not appear to have an effect on position (i.e., participants were generally biased slightly towards the smaller hoop).

```{r PltHoopSizeEstimates, include = T, echo = F, fig.asp=.45, fig.cap="_Posterior predictions for the mean standing position._"}
plt_estimates <- draws$plt_estimates
plt_estimates
```

@@

Add in facet plot

``` {r TwoThrowFacets, include = T, echo = F}
# process 
df_TwoThrow <- model_data_pos %>% 
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(HoopDelta)),
         slab_measures = factor(temp, labels = c("~90%", "~50% - 1", "~50%", "~50% + 1", "~50% + 2", "~10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(HoopDelta))

@@

```{r}

summary(Two_throw_m1)

@@

Add in facets

``` {r RewardFacets, include = T, echo = F}
df_Rewards <- model_data %>%
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(Norm_Delta)),
         slab_measures = factor(temp, labels = c("90%", "75%", "25%", "10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(Norm_Delta))

>>>>

```{r load data and source function Hoop Size, echo = F, include = F}
# load model data 
load("../Analyses/Experiment_3_Hoop_size/data/model_data")

@@

Figure \@ref(fig:HoopSizeFacets) shows the data for each or the participants. Each plot shows the standing position on every trial for each of the standardised distances the participants were tested at. The dots are set to be somewhat translucent so darker regions demonstrate the participant stood in this location more often. Anything above the dashed line demonstrates the participant shifting towards the smaller hoop, while below represents the participant opting to be closer to the big hoop.

```{r HoopSizeFacets, include=T, echo=F, fig.asp = .75, fig.cap = "_Facet plots for the Hoop Size experiment_"}
load("../Analyses/Experiment_3_Hoop_size/scratch/df_part2_norm")
df_hoopsize <- norm_dat
rm(norm_dat)

@@

### Modelling

@@

```{r run-model-hoop-size-priors, echo = T, include = T, message = F, warning = F, cache = TRUE}
# run model
Hoop_size_priors <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                        data = model_data,
                        family = "beta",
                        prior = c(set_prior("student_t(3, 0, 1)",
                                            coef = "norm_hoop_pos",
                                            class = "b"),
                                  set_prior("student_t(3,0,1)",
                                            class = "Intercept")),
                        cores = 2,
                        chains = 2,
                        iter = 5000,
                        warmup = 2500,
                        control = list(adapt_delta = .95, max_treedepth = 15),
                        sample_prior = "only")
```

```{r HoopSizePriors, include = F, echo = F, warning = F,  fig.asp = .45, fig.cap="_Prior predictions for the Hoop Size experiment_"}
# need to make a dataset
draws <- HS_draw_post(Hoop_size_priors, model_data)

plt_prior_hoopsize <- draws$plt_estimates + 
  scale_x_continuous(expression(paste("Normalised ", Delta)), 
                                breaks = c(0,.5,1),
                                labels = c("Big Hoop", "Centre", "Small Hoop")) + 
  theme(legend.position = "bottom")

@@

```{r run-model-Hoop-size, include = T, echo = T, message = F, warning = F, cache = TRUE}
# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                    data = model_data,
                    family = "beta",
                    prior = c(set_prior("student_t(3, 0, 1)",
                                        coef = "norm_hoop_pos",
                                        class = "b"),
                              set_prior("student_t(3,0,1)",
                                        class = "Intercept")),
                    cores = 2,
                    chains = 2,
                    iter = 5000,
                    warmup = 2500,
                    control = list(adapt_delta = .95, max_treedepth = 15))

@@

```{r PltHoopSizeEstimates, include = F, echo = F, fig.asp=.45, fig.cap="_Posterior predictions for the mean standing position._"}
plt_post_hoopsize <- draws$plt_estimates + 
  scale_x_continuous(expression(paste("Normalised ", Delta)), 
                                breaks = c(0,.5,1),
                                labels = c("Big Hoop", "Centre", "Small Hoop")) + 
  theme(legend.position = "bottom")
```

The model results confirmed that participants in general had a bias towards standing closer to the small hoop (mean of `r round(HDI_all$mean, digits = 3)`, 95% HDPI of |`r round(HDI_all$lower, digits = 3)`, `r round(HDI_all$upper, digits = 3)`|). We can be reasonably confident about this results as the p(x > 0.5|data) = `r paste(round(p_above_5$above0_5, digits = 3)*100, "%", sep = "")`. This can be seen in the posterior in the right hand plot of Figure \@ref(fig:PltHoopSize). Also, note that distance did not appear to have an effect on position (i.e., participants were generally biased slightly towards the smaller hoop).

``` {r PltHoopSize, include = T, echo = F, fig.asp = .45, fig.cap="_Figure on the left shows the Prior predictions. The figure on the right shows the Posterior predictions once the model had been conditioned on the data_"}

gridExtra::grid.arrange(plt_prior_hoopsize, plt_post_hoopsize, ncol = 2)
```
## Experiment 2: Two Throws

@@

Figure \@ref(fig:TwoThrowFacets) shows the individual data for each of the participants in this experiment. Each plot shows where the participants stood on each trial for each of the distances they were tested at with the different conditions being colour coded.

``` {r TwoThrowFacets, include = T, echo = F, fig.asp = .75, fig.cap = "_Facet plots for each participant in the Two Throw experiment_"}
# process 
df_TwoThrow <- model_data_pos %>% 
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(HoopDelta)),
         slab_measures = factor(temp, labels = c("~90%", "~50% - 1", "~50%", "~50% + 1", "~50% + 2", "~10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(HoopDelta))

@@

```{r, echo = F, include = T}

fixef(Two_throw_m1)

@@

Figure \@ref(fig:RewardFacets) shows the individual data for each of the participants in this experiment. Each plot shows where the participants stood on each trial for each of the distances at which they were tested with the different conditions being colour coded.

``` {r RewardFacets, include = T, echo = F, fig.asp = .75, fig.cap = "_Facet plots for the Rewards experiment_"}
df_Rewards <- model_data %>%
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(Norm_Delta)),
         slab_measures = factor(temp, labels = c("90%", "75%", "25%", "10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(Norm_Delta))
